### 2025-03-12 paper/sections/other/compute.qmd
Add two points in 5.2 limitations

For tuning of selected hyperparameters, we distributed the task of generating counterfactuals during training across 40 CPUs with 2GB memory each for all tabular datasets. Except for the *Adult* dataset, all training runs were completed in less that half an hour (<0h30m). The *Adult* dataset took around 0h35m to complete. For *MNIST*, we relied on 100 CPUs with 2GB memory each.

>>>>

For tuning of selected hyperparameters, we distributed the task of generating counterfactuals during training across 40 CPUs with 2GB memory each for all tabular datasets. Except for the *Adult* dataset, all training runs were completed in less that half an hour (<0h30m). The *Adult* dataset took around 0h35m to complete. Evaluations across 20 CPUs with 3GB memory each generally took less than 0h30m to complete. For *MNIST*, we relied on 100 CPUs with 2GB memory each. For the *MLP*, training of all models could be completed in 1h30m, while the evaluation across 20 CPUs (6GB memory) took 4h12m. For the *CNN*, training of all models took ~8h, with conventionally trained models taking ~0h15m each and model with CT taking ~0h30m-0h45m each.

### 2025-03-12 paper/sections/other/tuning.qmd

Based on the findings from our initial large grid searches (@sec-app-grid), we tune selected hyperparameters for all datasets.

>>>>

Based on the findings from our initial large grid searches (@sec-app-grid), we tune selected hyperparameters for all datasets: namely, the decision threshold $\tau$ and the strength of the energy regularization $\lambda_{\text{reg}}$. The final hyperparameter choices for each dataset are presented in **ADD TABLE**. Detailed results for each data set are shown in **ADD FIGURES**. From **ADD TABLE**, we notice that the same decision threshold of $\tau=0.5$ is optimal for all but on dataset. We attribute this to the fact that a low decision threshold results in a higher share of mature counterfactuals and hence more opportunities for the model to learn from examples. This has played a role in particular for our real-world tabular datasets and MNIST, which suffered from low levels of maturity for higher decision thresholds. In cases where maturity is not an issue, as for *Moons*, higher decision thresholds lead to better outcomes, which may have to do with the fact that the resulting counterfactuals are more faithful to the model. Concerning the regularization strength, we find somewhat high variation across datasets. Most notably, we find that relatively low levels of regularization are optimal for MNIST. We hypothesize that this finding may be attributed to the uniform scaling of all input features (digits). Finally, to increase the proportion of mature counterfactuals for some datasets, we have also investigated the effect on the learning rate $\eta$ for the counterfactual search, but found little effect on the results.
